Number of COVID-19 Cases in Canada By Region, Age, and Sex

### 2024-11-26 paper/paper.qmd
Updated references

# Visualization with Density Plots
ggplot(filtered_data, aes(x = Predicted_Probability, fill = Region)) +
  geom_density(alpha = 0.6) + # Density plot for predicted probabilities
  facet_wrap(~Region, scales = "free") + # Separate density plots by region
  labs(
    title = "Density of Predicted Probability of High Risk by Region",
    x = "Predicted Probability of High Risk",
    y = "Density"
  ) +
  scale_fill_manual(
    values = c("Urban" = "lightgreen", "Rural" = "yellow") 
  ) +
  theme_minimal()

>>>>

# Visualization with Density Plots
ggplot(filtered_data, aes(x = Predicted_Probability, fill = Region)) +
  geom_density(alpha = 0.6) + # Density plot for predicted probabilities
  facet_wrap(~Region, scales = "free") + # Separate density plots by region
  labs(
    title = "",
    x = "Predicted Probability of High Risk",
    y = "Density"
  ) +
  scale_fill_manual(
    values = c("Urban" = "lightgreen", "Rural" = "yellow") 
  ) +
  theme_minimal()
